Twisted \(M\)-theory and its perturbative quantization.

### 2021-01-27 paper.tex
L_\infty map from IIA to potentials

Before recalling this conjecture, we first fix some notation which is useful to describe the state space for the Type IIA string.
For $i,j$ integers define the space of $(i,j)$-polyvector fields to be
\[
  \pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX)
\]
where $TX$ is the holormorphic tangent bundle.
Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields $\PV^{i}_{\rm hol}(X)$ of type $i$.

@@

This equipped $\cE_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory.
It's relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.

@@

\subsubsection{Eight-dimensional Kodaira--Spencer theory}
\label{sec:orgeb2dd4d}
\subsection{The Type IIA topological string}
\label{IIAtop}
\subsection{Reduction of twisted supergravity}
\label{sec:orgcf7b6a4}
\subsubsection{Calabi--Yau compactifications}
\label{sec:org16a2c98}
\subsection{Twisted supergravity on a three-fold}
\label{sec:org774abb4}
\section{The non-minimal G2 twist}
\label{sec:org590ab85}

>>>>

Before recalling this conjecture, we first fix some notation which is useful to describe the state space for the Type IIA string. \surya{move earlier?}
For $i,j$ integers define the space of $(i,j)$-polyvector fields to be
\[
  \pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX)
\]
where $TX$ is the holormorphic tangent bundle.
Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields $\PV^{i}_{\rm hol}(X)$ of type $i$.

@@

This equips $\cE_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory.
Its relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.

@@

\subsubsection{Eight-dimensional Kodaira--Spencer theory}
\label{sec:orgeb2dd4d}

Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\Z/2$-graded theory with the following fundamental fields:
\begin{itemize}
\item The even fields are a holomorphic function $\mu^0$ and a $\partial$-closed holomorphic bivector $\mu^2$.
\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\partial$-closed holomorphic section $\mu^3$ of $\wedge^3 T_X$.
\end{itemize}

The space of fields admits a locally free description obtained by including the ``descendants" \surya{maybe should be more formal here}
The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
Here, $u^k \mu^j$ is a section of $\PV^{j - k, \bu}$.
The sheaf of cochain complexes $\cE$ underlying minimal Kodaira--Spencer theory on $X$ is
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \mu^0 \in \PV^{0,\bu} \\
& & \sum u^k \mu^1 \in \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
& \sum u^k \mu^2 \in  \PV^{2,\bu} \ar[r,"u \partial"] & u \PV^{1,\bu} \ar[r, "u \partial"] & u^2 \PV^{0,\bu} \\
\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \partial"]& u \PV^{2,\bu} \ar[r,"u \del"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\
\end{tikzcd}
\]
The differential on this sheaf of cochain complexes is given by $\dbar + u \partial$.

There is a local Lie algebra structure on $\Pi\cE$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
On the fields (including the descendants) it is defined by the formula
\[
[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} \{\mu^i, \mu^j\}_{\rm NS} .
\]

The space of fields of minimal Kodaira--Spencer theory $\cE_{\rm KS}$ is equipped with an odd Poisson tensor defined by
\[
\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
\]
Together with the local Lie algebra structure, this data equips $\cE_{\rm KS}$ with the structure of a $\Z/2$-graded Poisson BV theory.

As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
The underlying sheaf of cochain complexes is
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \eta^{0}\in\PV^{0,\bu} \\
& & \mu^{1}+u\mu^{0}\in\PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
u^{-1} \gamma^4 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
\beta^{4} \in\PV^{4,\bu} &  &  & \\
\end{tikzcd}
\]
We will again refer to this sheaf as $\cE_{\rm pot}$. Note that we can identify $cE_{\rm pot}\cong \Pi T^{*}(\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu}))$.

\begin{dfn}
  Let $X$ be a Calabi-Yau 4-fold, and let $\mc L$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket. Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\mc L$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}

To facillitate the calculations in this section, it will be useful to explicate the Lie structure. We have the following brackets:

\begin{align}
  \PV^{1,\bu}\times\PV^{0,\bu}\to \PV^{0,\bu},\ \ \ & [\mu^{1},\nu^{0}] = \{\mu^{1},\nu^{0}\}_{NS}\\
  \PV^{1,\bu}\times\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS}\\
  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS}
  \PV^{3,\bu}\times \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
  \PV^{4,\bu}\times \PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [\beta^{4}, \nu^{0}] = \{\beta^{4}, \nu^{0}\}_{\rm {NS}}\\
  \PV^{3,\bu}\times \PV^{0,\bu}\to \PV^{1,\bu}, \ \ \ & [\gamma^{3}, \nu^{0}] = \{\partial\gamma^{3}, \nu^{0}\}_{\rm NS}\\
  \PV^{3,\bu}\times \PV^{1,\bu}\to \PV^{3,\bu}, \ \ \ & [\gamma^{3}, \mu^{1}] = \{\gamma^{3}, \mu^{1}\}_{\rm NS}\\
  u^{-1}\PV^{4,\bu}\times u\PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [u^{-1}\gamma^{4}, u\mu^{0}] = \{\gamma^{4},\mu^{0}\}_{\rm NS}
\end{align}
\surya{explain more}

Together with the wedge and integrate pairing, $\cE_{\rm pot}$ has the structure of a nondegenerate BV theory.

Like in the case of Kodaira--Spencer theory on a complex surface, there is a  map of sheaves of cochain complexes $\Phi^{(1)}: \cE_{\rm pot}\to \cE_{\rm KS}$ given by

\[\begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ u^{-1}\gamma^{4}+\gamma^{3} \\ \beta^{4}\end{pmatrix}\mapsto \begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ \partial\gamma^{3} \\ \partial\beta^{4}\end{pmatrix}\]

This fails to be a map of local dg Lie algebras, but the induced map on $\partial$-cohomology is indeed a map of local Lie algebras. Therefore, we still have the following:

\begin{prop}
There is a local $L_{\infty}$ map $\cE_{\rm pot}\to \cE_{\rm KS}$.
\end{prop}
\begin{proof}
  Consider the collection of linear maps $\{\Phi^{(n)}: \cE_{\rm Pot}^{\otimes n}\to \cE_{\rm KS}[n-1]\}$ where $\Phi^{(1)}$ is given as above and $\Phi^{{(2)}}$ is given by \[\begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ u^{-1}\gamma^{4}+\gamma^{3} \\ \beta^{4}\end{pmatrix}\otimes \begin{pmatrix}\tilde{\nu}^{0} \\ \tilde{\mu}^{1}+u\tilde{\mu}^{0}\\ u^{-1}\tilde{\gamma}^{4}+\tilde{\gamma}^{3} \\ \tilde{\beta}^{4} \end{pmatrix}\to \begin{pmatrix} 0 \\ 0 \\ [\mu^{0},\tilde{\gamma}^{3}]_{\rm NS}\pm [\tilde{\mu}^{0},\gamma^{3}] \\ 0\end{pmatrix}.\]

  We claim that the $\Phi^{(n)}$ define an $L_{\infty}$ map. To this end, there are three kinds of conditions to check.
  \begin{itemize}
    \item A 2-linear condition which expresses that $\Phi^{(2)}$ renders the failure of $\Phi^{(1)}$ to preserve the brackets homotopically trivial. That is, for $a,b\in\cE_{\rm Pot},$ \[\Phi^{(1)}([a,b])-[\Phi^{(1)}(a),\Phi^{(1)}(b)]=d_{\rm KS}\Phi^{(2)}(a,b)-\Phi^{(2)}(d_{\rm Pot}a, b)-(-1)^{|a|}\Phi^{(2)}(a,d_{\rm Pot}b).\] Note that $\Phi^{(1)}$ in fact preserves all brackets other than the brackets $\PV^{3,\bu}\otimes \PV^{1,\bu}\to \PV^{3,\bu}$ and $u^{-1}\PV^{4,\bu}\otimes u\PV^{0,\bu}\to \PV^{3,\bu}$
      \surya{to finish}
  \end{itemize}
\end{proof}

\subsection{The Type IIA topological string}
\label{IIAtop}
\subsection{Reduction of twisted supergravity}
\label{sec:orgcf7b6a4}
\subsubsection{Calabi--Yau compactifications}
\label{sec:org16a2c98}
\subsection{Twisted supergravity on a three-fold}
\label{sec:org774abb4}
\section{The non-minimal G2 twist}
\label{sec:org590ab85}
